SPARQL on the Open, Decentralised Web

### 2016-07-23 dissertation/introduction.tex
Notes on IRI scheme

Note that all the IRIs uses the HTTP schema. The Hypertext Transfer
Protocol (HTTP) is the main application protocol used on the Internet
for the Web, and is also the protocol used most for the Semantic
Web. It is a request-response protocol in a client-server computing
model, but also accommodates for intermediate proxies. HTTP messages
consist of a header, typically with metadata, and a body, which is the
content itself. The standard defines several headers that can be used
to control caching on either the client, the server or an intermediate
proxy.

@@

>>>>

Note that all the IRIs uses the HTTP scheme. The Hypertext Transfer
Protocol (HTTP) is the main application protocol used on the Internet
for the Web, and is also the protocol used most for the Semantic
Web. It is a request-response protocol in a client-server computing
model, but also accommodates for intermediate proxies. HTTP messages
consist of a header, typically with metadata, and a body, which is the
content itself. The standard defines several headers that can be used
to control caching on either the client, the server or an intermediate
proxy.

@@

HTTP IRIs are not the only possible choice, to the contrary, the
scheme and what may be associated with it, such as a protocol, is an
orthogonal issue to the data model and syntax, and any IRI scheme can
be used.
